Nitrogen cycling in the CLM5: controls on responses to environmental forcing

### 2018-11-09 SIfigs.tex
Updates from ShareLaTeX

 \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/frac_deviation_p1CLM5_CAX__y1.png}
     \caption{Caxiuana State Parameter Sensitivity}
     \label{CAX state}
  \end{figure}

   \begin{figure}[h]
     \centering
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/frac_deviation_p1CLM5_BCI__y1.png}
     \caption{BCI State Parameter Sensitivity}
     \label{BCI state}
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/frac_deviation_p1CLM5_ORN__y1.png}
     \caption{Oak Ridge State Parameter Sensitivity}
     \label{ORN state}
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/frac_deviation_CO2_response_1CLM5_1x1pt_Br-cax_ens_transient_ELEV_PI_y1.png}
     \caption{Caxiuana CO2 response}
     \label{Caxiuana CO2 response Parameter Sensitivity }
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/frac_deviation_CO2_response_1CLM5_1x1pt_US-ORN_ens_transient_ELEV_PI_y1.png}
     \caption{Oak Ridge CO2 response}
     \label{Oak Ridge CO2 response Parameter Sensitivity}
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/frac_deviation_CO2_response_1CLM5_BCI__y1.png}
     \caption{BCI CO2 response}
     \label{BCI CO2 response Parameter Sensitivity}
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/rel_GPP.png}
     \caption{GPP CO2 and N respones}
     \label{GPP CO2 and N respones}
  \end{figure}

 \begin{figure}[h]
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/rel_NPP.png}
     \caption{NPP CO2 and N respones}
     \label{NPP CO2 and N respones}
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/rel_LAI.png}
     \caption{LAI CO2 and N respones}
     \label{LAI CO2 and N respones}
  \end{figure}

>>>>

\begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_STATE_1CLM50defpft_trans_1x1pt_Br-cax_ens_MIC_y1.png}
     \caption{Caxiuana Forest State}
     \label{CAX state}
  \end{figure}

 \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_STATE_1CLM50defpft_trans_1x1pt_US-Me2_ens_MIC_y1.png}
     \caption{Metolius Forest State}
     \label{MET state}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_STATE_1CLM50defpft_trans_1x1pt_US_Ha1_ens_MIC_y1.png}
     \caption{Harvard Forest State}
     \label{HVF state}
  \end{figure}

 \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_celev_1x1pt_US_Ha1_ens_MIC_p1.png}
     \caption{Harvard Forest Nitrogen Fertilization}
     \label{HRV ndep}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_ndep_1x1pt_US_Ha1_ens_MIC_p1.png}
     \caption{Harvard Forest CO2 Fertilization}
     \label{HRV celev}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_celev_1x1pt_Br-cax_ens_MIC_p1.png}
     \caption{Caxiuana Forest Nitrogen Fertilization}
     \label{CAX ndep}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_ndep_1x1pt_Br-cax_ens_MIC_p1.png}
     \caption{Caxiuana Forest CO2 Fertilization}
     \label{CAX celev}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_ndep_1x1pt_US_Ha1_ens_MIC_p1.png}
     \caption{Metolius Forest Nitrogen Fertilization}
     \label{MET ndep}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_celev_1x1pt_US-Me2_ens_MIC_p1.png}
     \caption{Metolius Forest CO2 Fertilization}
     \label{MET celev}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_celev_1x1pt_US-NR1_ens_MIC_p1.png}
     \caption{Niwot Forest Nitrogen Fertilization}
     \label{NR1 ndep}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_ndep_1x1pt_US-NR1_ens_MIC_p1.png}
     \caption{Niwot Forest CO2 Fertilization}
     \label{NR1 celev}
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/NOVc_CNdep_GPP1__p2012.png}
     \caption{GPP CO2 and N respones}
     \label{GPP CO2 and N respones 2001}
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/NOVc_CNdep_NPP1__p2012.png}
     \caption{NPP CO2 and N respones}
     \label{NPP CO2 and N respones 2001}
  \end{figure}

 \begin{figure}[h]
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/OCT_CNdep_NPP1_CLM50defpft_ndep_1x1pt_US-Me2_ens_MIC_p2006.png}
     \caption{NPP CO2 and N respones}
     \label{NPP CO2 and N respones}
  \end{figure}

   \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/NOVc_CNdep_TLAI1__p2012.png}
     \caption{LAI CO2 and N respones}
     \label{LAI CO2 and N respones 2001}
  \end{figure}

   \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/NOVc_CNdep_TOTVEGC1__p2012.png}
     \caption{VEGC CO2 and N respones}
     \label{VEGC CO2 and N respones 2001}
  \end{figure}

   \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/NOVc_CNdep_LEAFN1__p2012.png}
     \caption{Leaf Nitrogen CO2 and N respones}
     \label{Leaf N CO2 and N respones 2001}
  \end{figure}
